Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-13 PDFpaper.qmd
paper rendered

---
title: Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns
author:
  - name: Grace Bridge
lightbox: true
---

@@

![Evening Grosbeak image](eg_pic.jpeg)
<!-- {.lightbox} -->
<!-- <img src="eg_pic.jpeg" alt="Evening Grosbeak image" width="400"/> -->

@@

<!-- <img src="egmap.jpeg" alt="Evening Grosbeak range map" width="400"/> -->
![Evening Grosbeak Range Map](egmap.jpeg)

@@

![Default Shiny App](default_shiny.png)

@@

![Iris dropdown menus Shiny App](iris_dropdown.png)
![Dropdown menu](dropdown.png)

@@

```{r, echo=TRUE, include=TRUE, error=FALSE, warning=FALSE, message=FALSE, eval = TRUE}
#| code-fold: show
#| code-summary: "Click to show leaflet code"
library(leaflet)

@@

@@

![Interactive Evening Grosbeak Platform](deployments.png)

@@

![Deployments map](output-onlinegiftools.gif)

@@

![Chosen bird map](chosenbird.png)

@@

![Chosen group map](chosengroup.png)

@@

![Winter roosting location map](wintermap.png)

![Winter roosting group map](wintergroups.png)

@@

![Data table page](data.png)

@@

![Bird 75503.45382](southamerica.png)

@@

"About Motus." <em>Motus</em>. <a>https://motus.org/about/</a>. Accessed 11 May 2024. <br>
"An R Interface to Leaflet Maps." <em>Leaflet</em>. <a>https://rstudio.github.io/leaflet/</a>. Accessed 11 May 2024. <br>
"Evening Grosbeak." <em>CornellLab</em> <a>https://www.allaboutbirds.org/guide/Evening_Grosbeak/id</a>. Accessed 11 May 2024. <br>
"Motus." <em>Motus</em>. <a>https://motuswts.github.io/motus/index.html</a>. Accessed 11 May 2024. <br>
"Welcome to Shiny." <em>Shiny</em> <a>https://shiny.posit.co/r/getstarted/shiny-basics/lesson1/index.html</a>. Accessed 11 May 2024. <br>
"What is R?." <em>R Project</em>. <a>https://www.r-project.org/about.html</a>. Accessed 11 May 2024.

>>>>

---
title: Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns
author:
  - name: Grace Bridge
format: pdf
---

```{r, include=FALSE}
## load packages
library(leaflet)
library(htmlwidgets)
library(webshot)
```

@@

![Evening Grosbeak image](eg_pic.jpeg){.lightbox width=50%}
<!-- {.lightbox} -->
<!-- <img src="eg_pic.jpeg" alt="Evening Grosbeak image" width="400"/> -->

@@

<!-- <img src="egmap.jpeg" alt="Evening Grosbeak range map" width="400"/> -->
![Evening Grosbeak Range Map](egmap.jpeg){.lightbox width=50%}

@@

![Default Shiny App](default_shiny.png){.lightbox width=50%}

@@

![Iris dropdown menus Shiny App](iris_dropdown.png){.lightbox width=50%}
![Dropdown menu](dropdown.png){.lightbox width=50%}

@@

```{r, echo=TRUE, include=TRUE, error=FALSE, warning=FALSE, message=FALSE, eval = FALSE}
#| code-fold: show
#| code-summary: "Click to show leaflet code"
library(leaflet)

@@

![Leaflet map](leaflet_screenshot.png){.lightbox width=60%}

@@

![Interactive Evening Grosbeak Platform](deployments.png){.lightbox width=50%}

@@

![Deployments map](gif_shot.png){.lightbox width=50%}

@@

![Chosen bird map](chosenbird.png){.lightbox width=50%}

@@

![Chosen group map](chosengroup.png){.lightbox width=50%}

@@

![Winter roosting location map](wintermap.png){.lightbox width=50%}

![Winter roosting group map](wintergroups.png){.lightbox width=50%}

@@

![Data table page](data.png){.lightbox width=50%}

@@

![Bird 75503.45382](southamerica.png){.lightbox width=50%}

@@

- "About Motus." <em>Motus</em>. <a>https://motus.org/about/</a>. Accessed 11 May 2024. <br>
- "An R Interface to Leaflet Maps." <em>Leaflet</em>. <a>https://rstudio.github.io/leaflet/</a>. Accessed 11 May 2024. <br>
- "Evening Grosbeak." <em>CornellLab</em> <a>https://www.allaboutbirds.org/guide/Evening_Grosbeak/id</a>. Accessed 11 May 2024. <br>
- "Motus." <em>Motus</em>. <a>https://motuswts.github.io/motus/index.html</a>. Accessed 11 May 2024. <br>
- "Welcome to Shiny." <em>Shiny</em> <a>https://shiny.posit.co/r/getstarted/shiny-basics/lesson1/index.html</a>. Accessed 11 May 2024. <br>
- "What is R?." <em>R Project</em>. <a>https://www.r-project.org/about.html</a>. Accessed 11 May 2024.
